Software Citation Principles

### 2016-04-05 sc-principles/software-citation-principles.tex
edits to use cases table to match Google Doc, addressing #105

Stakeholder & wants to 	&  \rot{Software name} & \rot{Author(s)} & \rot{Version number} & \rot{Release date} & \rot{Location\slash repository} & \rot{Unique identifier} & \rot{Indexed citations} & \rot{Contributor role} & \rot{Software license}  \\

@@

Researcher            & use someone else's software for a paper      & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             & \textbullet \\
Researcher            & use someone else's software for new software & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             & \textbullet \\
Researcher            & contribute to software                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet\\
Researcher            & find citations of software               & \textbullet &             &             &             &             & \textbullet & \textbullet &            & \\
Researcher            & get credit for software development          & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet  \\
Researcher            & ``reproduce'' analysis                   & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             &            & \textbullet \\
Researcher            & benchmark software                       & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             &            & \textbullet \\
Researcher            & find software to implement task          & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Publisher                  & publish software paper                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             & \\
Publisher                  & publish papers that cite software        & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \\
Indexer                     & build catalog of software               & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &            & \textbullet \\
Domain group           & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &            & \textbullet \\
Library\slash archive  & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &            & \textbullet \\
Repository                 & show scientific impact of holdings       & \textbullet &             &             &             &             & \textbullet & \textbullet &             &             \\
Funder                       & show how funded software has been used   & \textbullet &             &             &             &             & \textbullet & \textbullet &             &             \\
Evaluator                   & evaluate contributions of researcher   &                  & \textbullet &             & \textbullet &             & \textbullet & \textbullet & \textbullet &             \\

>>>>

Stakeholder & wants to 	& \rot{Unique identifier} &  \rot{Software name} & \rot{Author(s)} & \rot{Contributor role} & \rot{Version number} & \rot{Release date} & \rot{Location\slash repository} & \rot{Indexed citations} & \rot{Software license}  \\

@@

Researcher            & 1.\ use someone else's software for a paper      & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & 2.\ use someone else's software for new software & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 3.\ contribute to software                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 4.\ find citations of software               & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             \\
Researcher            & 5.\ get credit for software development      & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 6.\ ``reproduce'' analysis                   & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 7.\ benchmark software                       & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 8.\ find software to implement task          & \textbullet & \textbullet & \textbullet &             &             &             & \textbullet & \textbullet & \textbullet \\
Publisher             & 9.\ publish software paper                   & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             &             \\
Publisher             & 10.\ publish papers that cite software        & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             \\
Indexer               & 11.\ build catalog of software                & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet \\
Domain group\slash library\slash archive          & 12.\ build software catalog\slash registry                & \textbullet & \textbullet & \textbullet &             &             &             & \textbullet &             &             \\
Repository            & 13.\ show scientific impact of holdings       & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             \\
Funder                & 14.\ show how funded software has been used   & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             \\
Evaluator             & 15.\ evaluate contributions of researcher     & \textbullet &             & \textbullet & \textbullet &             & \textbullet &             & \textbullet &             \\
Citation manager      & 16.\ store software entry        			 & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             \\
